systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-03-03 paper/trunk/systemfit_code.tex
fixed quote characters
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@631 591db2bd-e0a0-4d22-8c19-2192dbb7da31
added paragraph in subsection "efficiency of the code" that explains how we compute "X' Omega^{-1}" without computing the (potentially huge) Omega^{-1} matrix
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@654 591db2bd-e0a0-4d22-8c19-2192dbb7da31

To calculate $\Omega^{-1}$ in sections~\ref{sec:Estimation}
and~\ref{sec:Restrictions} it is not necessary to invert
the (huge) $\Omega$ matrix,
because it is sufficient to invert the (small) $\Sigma$ matrix and
calculate it by $\Omega^{-1} = \Sigma^{-1} \otimes I$
\citep[p.\ 342]{greene03}.

>>>>

The matrix $\Omega^{-1}$ that is used to compute the estimated
coefficients and their covariance matrix is of size
$( G \cdot T ) \times ( G \cdot T )$
(see sections~\ref{sec:Estimation} and~\ref{sec:Restrictions}).
In case of large data sets, this matrix $\Omega^{-1}$ gets really huge
and needs a lot of memory.
Therefore, we use the following transformation and compute $X' \Omega^{-1}$
by deviding the $X$ matrix into submatrices,
doing some calculations with these submatrices,
adding up some of these submatrices, and
finally putting the submatrices together:
\begin{equation}
X' \Omega^{-1}
%= X' \left( \Sigma^{-1} \otimes I \right)
= \sum_{i=1} \left[
   {X^1}' \sigma^{1i} \quad {X^2}' \sigma^{2i}
   \quad \cdots \quad  \quad {X^G}' \sigma^{Gi}
\right]
\end{equation}
where $\sigma^{ij}$ are the elements of the matrix $\Sigma^{-1}$,
and $X^i$ is a submatrix of $X$ that contains the rows
that belong to the $i$'s equation.
